%% ==========================================================================
%%  CONTENT — Your actual resume data
%%  -----------------------------------------------------------------------
%%  This is the ONLY file you need to edit when updating your resume.
%%  Just modify entries, add new ones, or reorder sections.
%% ==========================================================================

% ========================== HEADER ========================================
\makeheader
    {Florian Braun}
    {AI \& Data Engineering \,\textbar\, Finance \,\textbar\, Entrepreneurship}
    {%
        \contactitem{\faIcon{phone-alt}}{+352\,661\,258\,898}%
        \contactsep%
        \contactlink{\faIcon{envelope}}{mailto:braunf25@proton.me}{braunf25@proton.me}%
        \contactsep%
        \contactitem{\faIcon{map-marker-alt}}{Leuven, Belgium}%
    }
    {%
        \contactlink{\faIcon{linkedin}}{https://www.linkedin.com/in/braunflorian25}{linkedin.com/in/braunflorian25}%
        \contactsep%
        \contactlink{\faIcon{globe}}{https://www.florianb.info}{florianb.info}%
    }

% ========================== SUMMARY =======================================
\section{Profile}

{\bodysize
AI \& Data Engineering specialist with interests spanning cybersecurity, business, and finance. Working at the intersection of technology and business, combining technical expertise in AI and data engineering with a strong understanding of financial markets. Developed skills through TryHackMe, DataCamp, Harvard's CS50, and Bloomberg Market Concepts, bringing both analytical rigour and strategic thinking to complex challenges.

\vspace{2pt}
Beyond technical work, runs two businesses --- Studio Grain (event photography) and Pulse Watch Co.\ (luxury watches) --- balancing creative vision with business execution. Multilingual (Dutch, French, English, German, Japanese), focused on building intelligent, secure systems that deliver real business value. Actively engaged with the tech and business communities through industry seminars, technical projects, and exploring graduate opportunities in computer science.
}

% ========================== EDUCATION =====================================
\section{Education}

\education{UC Leuven-Limburg}{Bachelor of Applied Science (BASc), Computer Science}{Sep 2024 -- Jun 2027}
\education{Harvard University}{Non-Degree Program --- CS50, Computer Science}{Sep 2024 -- Dec 2024}
\education{KU Leuven}{Bachelor of Science (BS), Computer Science}{Sep 2023 -- Sep 2024}
\education{KU Leuven}{Preparatory Math Week, Mathematics}{Sep 2023}
\education{European School of Luxembourg 1}{European Baccalaureate}{2012 -- Jul 2023}

% ========================== EXPERIENCE ====================================
\section{Experience}

\experience{Co-Founder}{Pulse Watch Co.}{Oct 2023 -- Present}{Leuven, Belgium}
\begin{bullets}
    \item Lead vision, strategy, and product development for a modern watchmaking brand combining timeless craftsmanship with contemporary design.
    \item Oversee full product lifecycle from concept to market launch, driving growth and brand presence in the lifestyle industry.
    \item Previously scaled early-stage ventures including a clothing brand (\textit{Core}) and cosmetics startup (\textit{Echo Studios}), building skills in product development, marketing, and growth strategy.
\end{bullets}

\experience{Founder \& Event Photographer}{Studio Grain}{Jan 2025 -- Present}{Leuven, Belgium}
\begin{bullets}
    \item Founded an independent studio specialising in event photography, beginning with film photography focused on natural lighting and authentic storytelling.
    \item Expanded to digital photography in June 2025 to enhance flexibility and coverage for large-scale events.
    \item Manage all aspects of the business end-to-end: client relations, on-site shooting, editing, branding, and delivery.
\end{bullets}

\experience{Head of Events}{Insignia --- UCLL International Student Association}{Jul 2025 -- Dec 2025}{Leuven, Belgium}
\begin{bullets}
    \item Led event planning and coordination for UCLL's international student community across a full semester of programming.
\end{bullets}
\subrole{Social Media Manager}{Sep 2024 -- Jun 2025}
\begin{bullets}
    \item Managed Insignia's online presence, overseeing content creation and engagement for UCLL's international student community.
\end{bullets}

\experience{Head of IT Department}{Pupils' Committee --- European School of Luxembourg 1}{Sep 2022 -- Jun 2023}{Luxembourg}
\begin{bullets}
    \item Led all IT operations, specialising in website development and ensuring smooth digital functionality across the organisation.
\end{bullets}

% ========================== PROJECTS ======================================
\section{Projects}

\project{Independent \& Algorithmic Trader}{Oct 2023 -- Present}
\begin{bullets}
    \item Manage a self-directed investment portfolio focused on equities (stocks, ETFs) and commodities, applying disciplined trading strategies.
    \item Conduct fundamental and technical analysis to identify market opportunities.
\end{bullets}

\project{European Synbio Hackathon}{Nov 2024}
\begin{bullets}
    \item Participated in the Read Write Grow Hackathon focused on biotech innovation.
    \item Co-created \textit{You Are What You Eat}, an AI-powered tool that analyses and breaks down food to better understand its components.
\end{bullets}

% ========================== ORGANISATIONS =================================
\section{Organisations}

\organisation{Insignia's Culture Fest}{Head of Logistics}{Oct 2025 -- Present}{Insignia}
\begin{bullets}
    \item Lead the logistics and coordination efforts for Insignia's Culture Fest, ensuring smooth event execution and operational efficiency.
\end{bullets}

\organisation{Pupils' Committee Sports}{Front-End Developer}{Nov 2022 -- Jun 2023}{European School of Luxembourg 1}
\begin{bullets}
    \item Built and maintained the front-end of the Pupils' Committee Sports website, ensuring an engaging and user-friendly experience.
\end{bullets}

\organisation{ESL1 IT Club}{Founder \& President}{Feb 2022 -- Feb 2023}{European School of Luxembourg 1}
\begin{bullets}
    \item Founded and led the ESL1 IT Club by organising events, coordinating projects, and creating learning opportunities for members.
    \item Mentored peers, ran workshops, and acted as the key contact for the club's IT initiatives and collaborations.
\end{bullets}

% ========================== VOLUNTEERING ==================================
\section{Volunteering}

\volunteer{Student Representative}{Digital Teaching and Learning Working Group}{Jan 2023 -- Jun 2023}{Education}
\begin{bullets}
    \item Helped integrate digitalisation into courses and the broader education system at the European School of Luxembourg 1, incorporating modern digital tools into the learning environment.
\end{bullets}

\volunteer{Guitarist}{Guitar Orchestra, Conservatoire Ville de Luxembourg}{Sep 2017 -- Jun 2020}{Arts and Culture}
\begin{bullets}
    \item Performed as a member of the Conservatoire's Guitar Orchestra, strengthening technical skills, musical interpretation, and ensemble collaboration.
\end{bullets}

% ========================== SKILLS ========================================
\section{Skills}

\skillcategory{Technical}{%
    \skilltag{Python}%
    \skilltag{AI / Machine Learning}%
    \skilltag{Data Engineering}%
    \skilltag{Web Development}%
    \skilltag{Front-End (HTML/CSS/JS)}%
    \skilltag{Git / GitHub}%
}

\skillcategory{Security \& Networking}{%
    \skilltag{Cybersecurity}%
    \skilltag{Network Security}%
    \skilltag{IPv6}%
}

\skillcategory{Finance}{%
    \skilltag{Technical Analysis}%
    \skilltag{Portfolio Management}%
    \skilltag{Financial Markets}%
}

\skillcategory{Business \& Creative}{%
    \skilltag{Product Development}%
    \skilltag{Brand Strategy}%
    \skilltag{Event Management}%
    \skilltag{Content Creation}%
    \skilltag{Photography}%
}

% ========================== CERTIFICATIONS ================================
\section{Certifications}

\begin{multicols}{2}
\begin{itemize}[leftmargin=15pt, itemsep=2pt, parsep=1pt, topsep=2pt]
    \bodysize
    \item \textbf{GitHub Foundations} \,{\color{subtle}--- GitHub}
    \item \textbf{Pre Security Certificate} \,{\color{subtle}--- TryHackMe}
    \item \textbf{IPv6 Sage Certification} \,{\color{subtle}--- Hurricane Electric}
    \item \textbf{AI Fundamentals} \,{\color{subtle}--- DataCamp}
    \item \textbf{Advent of Cyber 2025} \,{\color{subtle}--- TryHackMe}
    \item \textbf{Bloomberg Market Concepts} \,{\color{subtle}--- Bloomberg}
\end{itemize}
\end{multicols}

% ========================== COURSES =======================================
\section{Courses}

{\bodysize\textbf{Japanese Language Study} --- WaniKani (Kanji \& Vocabulary)}

% ========================== HONOURS =======================================
\section{Honours \& Awards}

\award{Finalist (Top 50) --- Future of IT Leaders: Data \& AI Challenge 2025}{Editx}{2025}

% ========================== LANGUAGES =====================================
\section{Languages}

\langentry{Native / Bilingual}{Dutch, French}%
\contactsep%
\langentry{Full Professional}{English}%
\contactsep%
\langentry{Elementary}{German, Japanese, Spanish}
