%% ==========================================================================
%%  EXAMPLE CONTENT — Copy this file to content.tex to get started
%%  -----------------------------------------------------------------------
%%  Replace the placeholder data below with your own information.
%%  This file demonstrates every available command and section type.
%% ==========================================================================

% ========================== HEADER ========================================
\makeheader
    {Jane Doe}
    {Software Engineering \,\textbar\, Machine Learning \,\textbar\, Product Design}
    {%
        \contactitem{\faIcon{phone-alt}}{+1\,555\,123\,4567}%
        \contactsep%
        \contactlink{\faIcon{envelope}}{mailto:jane.doe@example.com}{jane.doe@example.com}%
        \contactsep%
        \contactitem{\faIcon{map-marker-alt}}{San Francisco, CA}%
    }
    {%
        \contactlink{\faIcon{linkedin}}{https://www.linkedin.com/in/janedoe}{linkedin.com/in/janedoe}%
        \contactsep%
        \contactlink{\faIcon{globe}}{https://www.janedoe.dev}{janedoe.dev}%
    }

% ========================== SUMMARY =======================================
\section{Profile}

{\bodysize
Software engineer with 3+ years of experience building scalable web applications and machine learning pipelines. Passionate about clean code, user-centred design, and turning complex problems into elegant solutions.

\vspace{2pt}
Outside of work, contributes to open-source projects and mentors junior developers through community programmes.
}

% ========================== EDUCATION =====================================
\section{Education}

\education{Massachusetts Institute of Technology}{Master of Science (MS), Computer Science}{Sep 2020 -- Jun 2022}
\education{University of California, Berkeley}{Bachelor of Science (BS), Computer Science}{Sep 2016 -- Jun 2020}

% ========================== EXPERIENCE ====================================
\section{Experience}

\experience{Senior Software Engineer}{Acme Corp}{Jan 2023 -- Present}{San Francisco, CA}
\begin{bullets}
    \item Led the redesign of the core API gateway, reducing average response time by 40\% and improving system reliability.
    \item Mentored a team of 4 junior engineers, conducting weekly code reviews and pair programming sessions.
    \item Built an internal ML pipeline for anomaly detection, processing over 2M events per day.
\end{bullets}

\experience{Software Engineer}{StartupXYZ}{Jul 2022 -- Dec 2022}{Remote}
\begin{bullets}
    \item Developed and shipped a real-time analytics dashboard using React, D3.js, and WebSocket connections.
    \item Designed RESTful APIs serving 10K+ daily active users with 99.9\% uptime.
\end{bullets}
\subrole{Software Engineering Intern}{Jun 2021 -- Aug 2021}
\begin{bullets}
    \item Built a proof-of-concept recommendation engine using collaborative filtering techniques.
\end{bullets}

% ========================== PROJECTS ======================================
\section{Projects}

\project{Open-Source Contribution Tracker}{Mar 2023 -- Present}
\begin{bullets}
    \item Created a CLI tool in Python that aggregates and visualises open-source contributions across GitHub, GitLab, and Bitbucket.
    \item Published on PyPI with 500+ monthly downloads.
\end{bullets}

\project{AI-Powered Code Reviewer}{Nov 2022}
\begin{bullets}
    \item Built a prototype tool that uses large language models to automatically review pull requests and suggest improvements.
    \item Won 2nd place at the HackMIT hackathon.
\end{bullets}

% ========================== ORGANISATIONS =================================
\section{Organisations}

\organisation{Women in Tech Society}{Vice President}{Sep 2022 -- Present}{MIT}
\begin{bullets}
    \item Organised monthly tech talks and networking events with 100+ attendees.
\end{bullets}

\organisation{Open Source Club}{Member \& Contributor}{Sep 2018 -- Jun 2020}{UC Berkeley}
\begin{bullets}
    \item Contributed to 3 major open-source projects and led beginner-friendly workshops on Git and GitHub.
\end{bullets}

% ========================== VOLUNTEERING ==================================
\section{Volunteering}

\volunteer{Coding Mentor}{Code for All}{Jan 2023 -- Present}{Education}
\begin{bullets}
    \item Teach Python fundamentals to underrepresented high school students in weekly 2-hour sessions.
\end{bullets}

\volunteer{Event Organiser}{Local Hackathon Series}{Sep 2021 -- Jun 2022}{Science and Technology}
\begin{bullets}
    \item Coordinated logistics for 3 hackathon events with 200+ participants each.
\end{bullets}

% ========================== SKILLS ========================================
\section{Skills}

\skillcategory{Languages \& Frameworks}{%
    \skilltag{Python}%
    \skilltag{TypeScript}%
    \skilltag{React}%
    \skilltag{Node.js}%
    \skilltag{SQL}%
    \skilltag{Go}%
}

\skillcategory{Tools \& Platforms}{%
    \skilltag{Docker}%
    \skilltag{Kubernetes}%
    \skilltag{AWS}%
    \skilltag{Git / GitHub}%
    \skilltag{CI/CD}%
}

\skillcategory{Data \& ML}{%
    \skilltag{TensorFlow}%
    \skilltag{Pandas}%
    \skilltag{Spark}%
    \skilltag{Data Pipelines}%
}

% ========================== CERTIFICATIONS ================================
\section{Certifications}

\begin{multicols}{2}
\begin{itemize}[leftmargin=15pt, itemsep=2pt, parsep=1pt, topsep=2pt]
    \bodysize
    \item \textbf{AWS Solutions Architect} \,{\color{subtle}--- Amazon}
    \item \textbf{TensorFlow Developer} \,{\color{subtle}--- Google}
    \item \textbf{Kubernetes Administrator} \,{\color{subtle}--- CNCF}
    \item \textbf{Professional Scrum Master} \,{\color{subtle}--- Scrum.org}
\end{itemize}
\end{multicols}

% ========================== COURSES =======================================
\section{Courses}

{\bodysize\textbf{Machine Learning Specialization} --- Stanford Online (Coursera)}

% ========================== HONOURS =======================================
\section{Honours \& Awards}

\award{Dean's List (4 semesters)}{UC Berkeley}{2016 -- 2020}

% ========================== LANGUAGES =====================================
\section{Languages}

\langentry{Native}{English}%
\contactsep%
\langentry{Professional}{Spanish, Mandarin}%
\contactsep%
\langentry{Elementary}{French}
